Standalone Tactics using OpenTheory

### 2012-02-07 paper.tex
more on 2.1

<Example illustrates requirements of the proof assistant: be able to read proofs from articles, be able to write terms as articles, and some form of communication with external program or website>

The central concept in \OpenTheory is that of a \emph{theory package}, $\Gamma\rhd\Delta$, which proves that the set of theorems $\Delta$ logically derive from the set of assumptions $\Gamma$.
The basic unit\footnote{Composite theory packages are also possible.} for constructing theory packages is an \emph{article file}, which consists of instructions for a virtual machine whose operations include primitive inference rules of higher-order logic and basic term-manipulation.

@@

>>>>

The example illustrates the key requirements of the proof assistant: the ability to
\begin{enumerate}
\item \label{req:artr} replay proofs by reading \OpenTheory articles,
\item \label{req:artw} write terms as \OpenTheory articles, and,
\item \label{req:comm} communicate, for example over the web, with external programs.
\end{enumerate}

Items~\ref{req:artr} and \ref{req:artw} require implementation work for interpreting and constructing articles.
The central concept in \OpenTheory is that of a \emph{theory package}, $\Gamma\rhd\Delta$, which proves that the set of theorems $\Delta$ logically derive from the set of assumptions $\Gamma$.
An \emph{article file} is the basic unit\footnote{Composite theory packages are also possible.} for constructing theory packages.
It consists of instructions for a virtual machine whose operations include primitive inference rules of higher-order logic and basic term-manipulation.

The instructions allowed in an article file represent the \OpenTheory \emph{logical kernel}.
To read an article, a proof assistant performs the inferences and other instructions listed in the file.
The \OpenTheory kernel is very close to HOL Light's kernel.
It should be easy to read articles in any proof assistant that manipulates higher-order logic.

@@

<why is it good for communicating terms and theorems? fixes ontology...>
